\documentclass{resume} % requires resume.cls in the same directory

\usepackage[utf8]{inputenc}
\usepackage{hyperref}

\name{Fahimeh Orvati Nia}

% Contact info in ONE line (as requested)
\address{College Station, TX \;|\; \href{mailto:fahimehorvatinia@tamu.edu}{fahimehorvatinia@tamu.edu} \;|\; \href{https://scholar.google.com/citations?hl=en&user=NI_iB4sAAAAJ}{Google Scholar} \;|\; \href{https://www.linkedin.com/in/fahimeh-orvati-nia-40b727392/}{LinkedIn} \;|\; \href{https://github.com/fahimehorvatinia}{GitHub}}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}
{\bf Ph.D., Computer Engineering} (In Progress) \hfill {\em Jan 2025 -- Present}\\
Texas A\&M University, College Station, TX\\
Research Areas: AI, Computer Vision, Agricultural Imaging, Graph Neural Networks\\
Affiliated with Texas A\&M AgriLife Research Institute

{\bf M.Sc., Electrical Engineering} \hfill {\em Aug 2023 -- Jan 2025}\\
University of Notre Dame, IN, USA\\
Thesis: Time-series anomaly detection using GANs and pedestrian intention prediction with GNNs

{\bf B.Sc., Electrical Engineering} \hfill {\em Sept 2016 -- Jan 2020}\\
Amirkabir University of Technology, Tehran, Iran
\end{rSection}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\begin{rSection}{Experience}
{\bf Research Assistant, Texas A\&M AgriLife Research} \hfill {\em Jan 2025 -- Present}\\
\begin{itemize}
  \item Computer vision and AI-based analysis of agricultural multispectral imagery.
  \item Plant growth analysis and phenotyping using deep learning.
  \item Integrating multispectral imaging with low-field MRI for comprehensive crop analysis.
\end{itemize}

{\bf Teaching Assistant, University of Notre Dame} \hfill {\em Fall 2023 -- Spring 2024}\\
\begin{itemize}
  \item Courses: Introduction to Electrical Engineering; Signals and Systems.
  \item Developed course materials and supported students with assignments and projects.
\end{itemize}

{\bf Research Assistant, University of Tehran} \hfill {\em Jan 2022 -- June 2023}\\
\begin{itemize}
  \item Machine learning for classification and clustering of musical instruments.
\end{itemize}

{\bf IoT Developer, NOICT Company (INRA)} \hfill {\em July 2021 -- Oct 2021}\\
\begin{itemize}
  \item Wireless communication between IoT devices using the Zigbee protocol.
\end{itemize}

{\bf Teaching Assistant, Amirkabir University of Technology} \hfill {\em Sept 2020}\\
\begin{itemize}
  \item Guided students in designing control systems using MATLAB/Simulink.
\end{itemize}
\end{rSection}

%--------------------------------------------------------------------------------
%    PROJECTS
%--------------------------------------------------------------------------------
\begin{rSection}{Selected Projects}
{\bf Traffic-Aware Pedestrian Intention Prediction} \hfill {\em 2025}\\
Traffic-aware graph neural network architecture (TA-STGCN) for pedestrian intention prediction in dynamic traffic environments; evaluated on PIE dataset.

{\bf Agricultural Imaging and Phenotyping} \hfill {\em 2025 -- Present}\\
Computer vision and AI methods for analyzing multispectral imagery of horticultural crops; integrating multispectral imaging with low-field MRI for comprehensive phenotyping.

{\bf GAN-Based Anomaly Detection} \hfill {\em 2024}\\
Designed GAN-based models with custom loss functions for time-series anomaly detection with applications in smart meter systems and power grids.

{\bf Neighborhood Feature Aggregation for Remote Sensing} \hfill {\em 2025}\\
Proposed neighborhood-based feature aggregation (pooling) for remote sensing image classification, targeting agricultural and environmental monitoring.
\end{rSection}

%--------------------------------------------------------------------------------
%    PUBLICATIONS
%--------------------------------------------------------------------------------
\begin{rSection}{Selected Publications}
\begin{itemize}
  \item {\bf Fahimeh Orvati Nia}, Hai Lin. \textit{Traffic-aware pedestrian intention prediction}. American Control Conference (ACC), 2025. \href{https://arxiv.org/abs/2507.12433}{arXiv:2507.12433}
  \item {\bf Fahimeh Orvati Nia}, Joshua Peeples, et al. \textit{Neighborhood Feature Pooling for Remote Sensing Image Classification}. WACV 2026 Workshop on Earth Observation. \href{https://arxiv.org/abs/2510.25077}{arXiv:2510.25077}
  \item {\bf Fahimeh Orvati Nia}, S. Salehi, J. Peeples. \textit{Evaluating GAN-LSTM for Smart Meter Anomaly Detection in Power Systems}. TPEC 2026. \href{https://arxiv.org/abs/2601.09701}{arXiv:2601.09701}
  \item A. McFarland, L. Rossi, F. Nia, J. Peeples, A. Svyanek. \textit{Integrating Multispectral Imaging and Low-Field Magnetic Resonance Imaging for Comprehensive Phenotyping of Horticultural Crops}. HORTSCIENCE 60 (7), 2025.
\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\begin{rSection}{Skills}
{\bf Languages \& APIs:} Python, C++, MATLAB, LaTeX\\
{\bf ML \& CV Libraries:} PyTorch, TensorFlow, Keras, OpenCV\\
{\bf Developer Tools:} Git, Docker\\
{\bf Embedded Systems:} STM32, Raspberry Pi, Arduino
\end{rSection}

%----------------------------------------------------------------------------------------
%	ACTIVITIES / SERVICE
%----------------------------------------------------------------------------------------
\begin{rSection}{Activities and Service}
{\bf Peer Review:} LXAI-NeurIPS 2025; IEEE Robotics and Automation Letters (RA-L); ICRA 2026; ACC 2025; CCTA 2025\\
{\bf Student Mentoring:} Chloe Tiley; Sophia Martinez-Badillo; Michael Morse; Amran Kassaye; Nazar Oladepo
\end{rSection}

\begin{rSection}{Awards and Scholarships}
{\bf Top rank in Iranian National Entrance Exam for Master's programs} \hfill {\em (Awarded)}\\
{\bf PlantCV Workshop + NAPPN 2026 Travel Award} \hfill {\em 2026}
\end{rSection}

\end{document}
