\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{left=1.5cm,right=1.5cm,top=1.5cm,bottom=1.5cm}
\usepackage{enumitem}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}

\pagestyle{empty}

\begin{document}

\begin{center}
    \textbf{\huge FAHIMEH ORVATI NIA} \\
    \vspace{0.3cm}
    College Station, TX | \href{mailto:fahimehorvatinia@tamu.edu}{fahimehorvatinia@tamu.edu} | \href{https://scholar.google.com/citations?hl=en&user=NI_iB4sAAAAJ}{Google Scholar} | \href{https://www.linkedin.com/in/fahimeh-orvati-nia/}{LinkedIn} | \href{https://github.com/fahimehorvatinia}{GitHub}
\end{center}

\section*{EDUCATION}
\textbf{PhD, Computer Engineering} (In Progress) \\
Texas A\&M University, College Station, TX \hfill Jan 2025 -- Present \\
Research Areas: AI, Computer Vision, Agricultural Imaging, Graph Neural Networks \\
Affiliated with Texas A\&M AgriLife Research Institute \\

\textbf{M.Sc., Electrical Engineering} \\
University of Notre Dame, IN, USA \hfill Aug 2023 -- Jan 2025 \\
Thesis: Time-series anomaly detection using GANs and pedestrian intention prediction with GNNs \\

\textbf{B.Sc., Electrical Engineering (Control)} \\
Amirkabir University of Technology, Tehran, Iran \hfill Sept 2016 -- Jan 2020 \\

\section*{EXPERIENCE}
\textbf{Research Assistant, Texas A\&M AgriLife Research} \\
Working on computer vision and AI-based analysis of agricultural multispectral imagery. \hfill Jan 2025 -- Present \\

\textbf{Peer Reviewer, IEEE Control Systems Society Conferences} \\
Reviewed submissions for:
\begin{itemize}[noitemsep,leftmargin=*]
    \item \textit{American Control Conference (ACC) 2025}
    \item \textit{Conference on Control Technology and Applications (CCTA) 2025}
\end{itemize} \\

\textbf{Teaching Assistant, University of Notre Dame} \\
\textit{Courses:} Introduction to Electrical Engineering (Fall 2023), Signals and Systems (Spring 2024) \\

\textbf{Research Assistant, University of Tehran} \\
Worked on machine learning for the classification and clustering of musical instruments. \hfill Jan 2022 -- June 2023 \\

\textbf{IoT Developer, NOICT Company, Tehran, Iran} \\
Developed wireless communication between IoT devices using the Zigbee protocol. \hfill July 2021 -- Oct 2021 \\

\section*{SELECTED PUBLICATIONS}
\begin{itemize}[noitemsep,leftmargin=*]
    \item Fahimeh Orvati Nia, Hai Lin. \textit{Traffic-Aware Pedestrian Intention Prediction}. American Control Conference (ACC) 2025. \href{https://arxiv.org/abs/2507.12433}{arXiv:2507.12433}
    
    \item Fahimeh Orvati Nia, Joshua Peeples, et al. \textit{Neighborhood Feature Pooling for Remote Sensing Image Classification}. Under review at WACV 2026. \href{https://arxiv.org/abs/2510.25077}{arXiv:2510.25077}
    
    \item Fahimeh Orvati Nia, S. Salehi, J. Peeples. \textit{Evaluating GAN-LSTM for Smart Meter Anomaly Detection in Power Systems}. arXiv preprint arXiv:2601.09701, 2026.
    
    \item A. McFarland, L. Rossi, F. Nia, J. Peeples, A. Svyanek. \textit{Integrating Multispectral Imaging and Low-Field Magnetic Resonance Imaging for Comprehensive Phenotyping of Horticultural Crops}. HORTSCIENCE 60 (7), 2025.
\end{itemize}

\section*{SKILLS}
\textbf{Languages \& APIs:} Python, C++, MATLAB, LaTeX \\
\textbf{ML \& CV Libraries:} PyTorch, TensorFlow, Keras, OpenCV \\
\textbf{Developer Tools:} Git, Docker \\
\textbf{Embedded Systems:} STM32, Raspberry Pi, Arduino

\section*{HONORS AND AWARDS}
\begin{itemize}[noitemsep,leftmargin=*]
    \item National full undergraduate scholarship in Iran
    \item Ranked top in Computational Intelligence and Communication Systems courses during B.Sc.
    \item Top rank in Iranian National Entrance Exam for Master's programs
\end{itemize}

\end{document}
